% !TEX root = ../report.tex

\begin{abstract}
\noindent This project aims to develop co-operative robotic systems which effectively map and search an area using non-telemetric sensors and communication. This will allow the systems to perform in environments which hinder telemetry, such as caves or tunnels.  Each robot should be able to solve this problem individually; however, after the introduction of multiple robots to the area, they should be able coordinate their movements to distribute the task and solve the problem faster. The robots will be tested in a custom-made testing environment---likely taking the form of a simple maze with a target that must be located---and evaluated based on their performance both individually and co-operatively.

Detailed analysis of the electrical, software and mechanical design solutions are presented. The robots will use a differential drive system and will be designed and constructed with the necessary hardware to complete the task of exploring their maze-like environment in a distributed fashion. Computer vision systems on the robots will be used in conjunction with ultrasonic sensors to perceive the environment and identify other robots in the group, and incremental encoders and an inertial measurement unit will be used to track the robots position and orientation. Communication will be conducted over either Wi-Fi or Bluetooth systems, which will be artificially restricted to require line-of-sight, so as to simulate situations where global communication is not possible.

The report also contains extensive discussion of the project management approach used to properly coordinate the project team. The structure of the team and practices employed have been considered carefully and a detailed timeline developed to limit project risk.

\end{abstract}
