% !TEX root = ../report.tex

\section{Introduction}\label{introduction}
\thispagestyle{plain}
\subsection{Problem context}\label{introduction/context}
Using multiple co-operating robots can be a useful strategy when attempting
to complete tasks that can be parallelised, such as exploration of a large
area. Usually, this requires a centralised system that can properly coordinate
the efforts of the robots in accomplishing the task. However, in environments
where radio communication is impossible or severely restricted, such as underground
or in areas with high interference, the systems would be unable to complete
their task. In these circumstances, communication may be limited to
non-telemetric sensors that require line-of-sight. Therefore, intelligent
algorithms are required to co-operate effectively in environments where line-of-sight
is not always available.

Co-operative robotics can be used to solve a variety of tasks
more effectively than a more complex individual robot and introduces
distribution and redundancy into the system which can be
highly advantageous over single agent systems~\cite{dudek96}. This redundancy
can be mission critical in scenarios where a hazardous environment poses risks
to individual robots, and means that the loss of a single robot is not fatal to
the mission.

Previous research into co-operative robotics has focused on UAVs~\cite{khan18},
non-autonomous agents~\cite{jimenez18}, or made use of extensive communication,
such as by using the cloud~\cite{wensing2018cooperative}. This study will use
restricted non-telemetric communication (i.e., local communication between
neighbouring robots rather than communication over a central server). Co-operating
well under this limitation poses additional challenges, which need to be overcome
in order to allow collaborative robotic exploration of environments such as caves.
This application area was inspired in part by a recent incident necessitating cave
exploration and rescue in Thailand~\cite{bbcthailand}.

In order to abstract away the physical complexities of operating on difficult
terrain and allow research to focus on communication and problem-solving algorithms,
a toy problem has been devised for the robots to solve. This will take the form
of a simple maze which contains an target that needs to be found and identified
by the robots. The primary aim of the study is to construct multiple robots which can
navigate this maze and co-ordinate their efforts to find the target more quickly than
could be achieved by each robot individually.

An additional requirement is that the robots should be constructed using
inexpensive components. This is necessitated by the increased cost implied by the
need for multiple robots.

\subsection{Report outline}\label{introduction/outline}

The purpose of this report is to present the preparatory work
performed to date as well as our plan for the completion of the
project.

Chapter~\ref{background} gives an overview of the subject area and describes
a number of concepts relevant to robotics for the uninitiated reader.
A summary of the high-level design
decisions taken so far and their justifications can be found in
Chapter~\ref{design}. Finally, Chapter~\ref{plan} details our approach to
the management of the project and provides details of our expected
timeline and budget.
